Solar wind predictions for the Parker Solar Probe orbit

### 2017-08-16 paperMVVB/sections/content.tex
summary; version without figures added

\section{Summary and conclusions}

@@

We estimated solar wind median values during PSP’s first perihelion and modeled the values for PSP’s closest perihelia. The velocity and temperature values are clearly overestimated below \SI{20}{\Rs} in comparison with existing observations. This empirical model shows that solar wind acceleration and heating processes below \SI{20}{\Rs} limit the simple back-extrapolation from existing in situ measurements.

>>>>

\section{Summary and conclusions}
We obtained lognormal representations of the frequency distributions' shapes of the four key solar wind parameters magnetic field strength, proton velocity, density and temperature. We derived analytical relations for the parameters' solar activity dependencies and for their solar distance scaling. An empirical solar wind model was build from the combination of the obtained frequency distributions, SSN dependence relations and solar distance dependence functions, representing the solar wind's solar activity and distance behavior. This empirical model was fed with SSN predictions and extrapolated to the orbit of PSP. We estimated solar wind median values during PSP’s first perihelion and modeled the values for PSP’s closest perihelia.

The velocity and temperature values are overestimated below \SI{20}{\Rs} in comparison with existing observations. This shows that solar wind acceleration and heating processes below \SI{20}{\Rs} limit the simple back-extrapolation from existing in situ measurements.\\

@@
